PK object batch mode trial

### 2023-07-13 data-raw/batchMode_trial_gpm.Rmd
Updated the eval_tkstats method

get_winning_model(my_pk)

@@

# Saving some CSVs
# my_tkstats %>% write_csv(file = "data-raw/Pooled_TKstats.csv")
# my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")

@@

ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
              "OrdersOfMagnitude_2023-07-12.png"),
       height = 4, width = 4)

@@

my_AIC %>% group_by(Chemical, Species, method) %>%
  filter(if_any(contains("AIC"), ~ . == min(.)))

@@

>>>>

get_winning_model(my_pk)
eval_tkstats(my_pk)

@@

# Saving some CSVs
# my_tkstats %>% write_csv(file = "data-raw/Pooled_TKstats.csv")
# my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
# Loading CSVs
my_nca <- read_csv(file = "data-raw/NonCompartmentalAnalysis.csv")

@@

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "OrdersOfMagnitude_2023-07-12.png"),
       height = 4, width = 4)

@@

@@

```{r update_eval_kstats}

my_eval <- left_join(my_tkstats_red, my_nca_red) %>%
  filter(is.finite(AUC_inf.tkstats), is.finite(AUC_inf.nca)) %>%
  group_by(!!!my_pk$settings_data_info$nca_group)

my_eval %>%
  dplyr::select(AUC_inf.tkstats, AUC_inf.nca, Cmax.tkstats, Cmax.nca) %>%
  ungroup(Dose) %>%
  summarize(AUC_inf_RMSE = abs(mean(AUC_inf.tkstats) - mean(AUC_inf.nca)),
            Cmax_RMSE = abs(mean(Cmax.tkstats) - mean(AUC_inf.nca)))
